Modeling the Impact of Commodity Prices and Interest Rates on the CAD/USD Exchange Rate: An Analysis of Key Drivers Using Bank Rate and BCPI

### 2024-12-03 paper/paper.qmd
update preamble and correct paper typo

## Overview
For this study, three primary data sets were used to explore the relationship between the Canadian dollar (CAD) and U.S. dollar (USD) exchange rate, commodity prices (via the Bank of Canada Commodity Price Index - BCPI), and interest rates. The data was collected from multiple publicly available sources: weekly exchange rates between the CAD and USD, weekly BCPI data from the Bank of Canada, and the Bank of Canada’s weekly interest rates. The exchange rate data set provides the value of the CAD against the USD [@bankofcanada_daily_exchange_rates], while the BCPI data set includes subcategories such as the total BCPI, energy BCPI, and metal BCPI [@bankofcanada_bcpi]. The interest rates data set provides the weekly bank rates set by the Bank of Canada [@BankOfCanadaInterestRates]. The BCPI is categorized into various types, with particular focus on energy and metal BCPI, as these sectors are main export areas for Canada.

@@

Overall, the BCPI methodology provides useful information on Canadian pricing. However, its effectiveness may be impacted by data lags, the use of proxies for commodity production volumes, and periodic revisions..
\newpage
# References

>>>>

## Overview
For this study, three data sets were used to explore the relationship between the Canadian dollar (CAD) and U.S. dollar (USD) exchange rate, commodity prices (via the Bank of Canada Commodity Price Index - BCPI), and interest rates. The data was collected from multiple publicly available sources: weekly exchange rates between the CAD and USD, weekly BCPI data from the Bank of Canada, and the Bank of Canada’s weekly interest rates. The exchange rate data set provides the value of the CAD against the USD [@bankofcanada_daily_exchange_rates], while the BCPI data set includes subcategories such as the total BCPI, energy BCPI, and metal BCPI [@bankofcanada_bcpi]. The interest rates data set provides the weekly bank rates set by the Bank of Canada [@BankOfCanadaInterestRates]. The BCPI is categorized into various types, with particular focus on energy and metal BCPI, as these sectors are main export areas for Canada.

@@

Overall, the BCPI methodology provides useful information on Canadian pricing. However, its effectiveness may be impacted by data lags, the use of proxies for commodity production volumes, and periodic revisions.
\newpage

# References
